Shaping the Perception of a Robot by Cognitive Priming

### 2016-09-02 main.tex
Rewritten hypotheses

\begin{inparaenum}[\itshape a\upshape)]
Two nested research questions have been presented so far: \item can we
characterise the link between expectations regarding the cognitive
skills of a robot and the effective ascription of anthropomorphic features to
this robot; and \item to this end, can we develop and validate a robust behavioural and
\emph{in-the-moment} metric of anthropomorphism?  \end{inparaenum}

These two questions translate into several experimental hypotheses, whose design
was guided by the following high-level hypothesis: \emph{the more we ascribe cognitive
capabilities to an agent, the more likely we are to focus on its head (\ie the
brain) when interacting with it}. As such, this hypothesis naturally suggests an
eye-tracking-based investigation.

%Eye-tracking-based technique logically follows as an investigation mean, is a natural
%methodology to investigate this intuition. We hence design audio-visual stimuli
%that elicit different levels of cognitive ascription onto the robot while being
%identical in every other way.

Our baseline hypothesis \h{1} is that cognitive priming allows us to effectively create
stimuli that induce \emph{lower} or \emph{higher} attribution of human-likeness
to the robot. This hypothesis can be tested by asking
participants to rate the interactions depicted by the stimuli as being more
\emph{machine-like} or \emph{human-like}.

Secondly, we hypothesise that people with a higher tendency to anthropomorphise
robots will tend to physically look at robots and humans in similar ways, contrary to
people with a lower tendency to anthropomorphise (\h{2}). If this is verified,
it supports the idea that anthropomorphic attributions affect gaze patterns. The
hypothesis can be tested by correlating the participants' tendency to
anthropomorphise, measured from a standard questionnaire, with the comparative
gazing behaviour in two conditions (human task \vs robot task).

Third, we hypothesise that in the \emph{human-like} condition (which we
interpret as well as a higher ascription of cognitive skills to the robot), the participants' gaze will be directed
significantly more towards the head of the robot than in the \emph{machine-like}
condition (interpreted as a lower ascription of cognitive skills) (\h{3}). If verified, it
effectively means that the expectations held by the participants regarding the
cognitive capabilities of the robot are reflected by the eye fixations on the
head of the robot.  The hypothesis can be tested by comparing gaze fixations in
the two conditions (\emph{human-like} \vs \emph{machine-like}).

Finally, the hypothesis \h{4} proposes that manipulating cognitive expectations
affects the broader tendency to anthropomorphise robots, \ie whether observing one
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots in general. The hypothesis can be
tested by looking at pre- and post-experiment self-reports on the tendency to
anthropomorphise.

If all these hypotheses are verified, the findings can be summarised as follow:
\h{1} shows that our manipulation (based on cognitive priming) does effectively
elicit lower or higher expectations in terms of the cognitive capabilities of
the robot; \h{4} shows that these expectations influence our tendency to
anthropomorphise robots in general; in parallel, \h{3} shows that these same expectations
shape the way we look at the robot by eliciting specific eye fixations on the
head of the robot; finally, \h{2} suggests that the fixation on the head
reflects human-likeliness and supports the thesis that head fixation can be used
as a behavioural measure of anthropomorphism.

>>>>

As suggested in the previous section, we aim at verifying the following research
hypothesis \h{}: the level of anthropomorphism ascribed by a human to a robot can be
effectively assessed by measuring the human's gaze fixations on the robot's head.

Our methodology involves showing participants video stimuli that elicit
different levels of anthropomorphism, and measuring gaze fixations over the
course of the video clips. To be suitable for an eye-tracking experiment, the
video stimuli must be visually identical between conditions, and we therefore
rely on non-visual cues to elicit different anthropomorphic projections
(cognitive priming). The next section details this methodology.

This approach allows us to decompose the hypothesis \h{} into two simpler
hypotheses \h{1} and \h{2}:  we want first to verify that cognitive priming
enables us to effectively create stimuli that induce lower or higher attribution
of human-likeness to robots (\h{1}).  We need next to verify that in the case of
high anthropomorphic attributions, the participants' gaze will be directed
significantly more towards the head of the robot than in the case of low
anthropomorphic attributions (\h{2}).

If verified, these hypotheses would allow us to conclude that in a given
human-robot interaction situation, the more a human focuses on the robot's head,
the more the human ascribe anthropomorphic features to the robot.
\fixme{Attention, this conclusion seems to wrongly reverse the implication of
the hypotheses!}

%If verified, it
%effectively means that the expectations held by the participants regarding the
%cognitive capabilities of the robot are reflected by the eye fixations on the
%head of the robot.  The hypothesis can be tested by comparing gaze fixations in
%the two conditions (\emph{human-like} \vs \emph{machine-like}).

\vspace{1em}

Besides, our experimental design allows to examine two additional hypotheses:

\begin{itemize}
    \item people who tend to anthropomorphise a lot show gazing behaviours that
        are similar for humans and robots, while people who show a lower
        tendency to anthropomorphise do not look at robots and humans in the
        same way (\h{3}). If this is verified, this would confirm that our
        gazing behaviour towards agents is impacted by our tendency to
        anthropomorphise.

    \item the mere observation of a robot acting in an \emph{human-like}
        situation suffice to increase the level of
        anthropomorphic attributions to robots \emph{in general} (\h{4}).
\end{itemize}

%If all these hypotheses are verified, the findings can be summarised as follow:
%\h{1} shows that our manipulation (based on cognitive priming) does effectively
%elicit lower or higher expectations in terms of the cognitive capabilities of
%the robot; \h{4} shows that these expectations influence our tendency to
%anthropomorphise robots in general; in parallel, \h{3} shows that these same expectations
%shape the way we look at the robot by eliciting specific eye fixations on the
%head of the robot; finally, \h{2} suggests that the fixation on the head
%reflects human-likeliness and supports the thesis that head fixation can be used
%as a behavioural measure of anthropomorphism.
